### 2013-09-26 exact_learning/paper.tex
smallcaps for datasets, some more corrections by vlad

In this chapter, we investigate the necessity and consequences of these
approximations in the $1$-slack cutting-plane learning algorithm in the context of semantic
image segmentation. We show that despite inference being deemed intractable in
loopy superpixel models, we are able to learn a pairwise conditional random
field model using a structured support vector machine exactly for this task.
We evaluate our approach on the popular MSRC-21 and Pascal VOC datasets. Our
approach improves upon the state-of-the-art on the MSRC-21 dataset, and is
competative with comparable approaches on the Pascal VOC dataset.% and nyu?

@@

\subsection{Semantic Image Segmentation}
% TODO reference auf davor / intro?
Our main application is of course semantic segmentation and object class
segmentation. We evaluate the proposed learning approach on Pascal VOC 2013 and
MSRC-21

@@

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lc}
        \toprule
                    & Jaccard \\
        \cmidrule{1-2}
    Unary terms only &  27.5 \\
    Pairwise model (move making)& 30.2\\
    Pairwise model (exact) & 30.4\\
        \cmidrule{1-2}
    \citet{dann2012pottics} & 27.4\\
    \citet{krahenbuhl2012efficient} & 30.2\\
    \citet{krahenbuhlparameter} & 30.8\\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Accuracies on the Pascal VOC Dataset. We compare our approach
    against approaches using the same unary potentials.\tablabel{pascalacc}}

@@

\subsubsection{Pascal VOC 2010}
For the Pascal VOC 2010 dataset, we follow the procedure from \citet{krahenbuhl2012efficient}
in using the official ``validation'' set as our evaluation set, and splitting the training set again.
We use the unary potentials provided by the same work, and compare only against methods
using the same setup and potentials, \citet{krahenbuhlparameter} and \citet{dann2012pottics}.
Note that state-of-the-art approaches, some not build on the CRF framework, obtain
around a Jaccard Index (also call VOC score) of 40\% , notably \cite{xia2012segmentation}, who 
evaluate on the Pascal VOC 2010 ``test'' set.

@@

Results on the Pascal-VOC dataset are shown in \Tabref{pascalacc}.
We compare against several approaches using the same unary potentials.
For completeness, we also list state-of-the-art approaches not based on CRF models.
Notably, out model matches or exceeds the performance of the much more involved approaches of
\citet{krahenbuhl2012efficient} and \citet{dann2012pottics} which use the same
unary potentials.
Using exact learning and inference slightly increased performance on this dataset.
Learning took 25 minutes using move-making alone and 100 minutes to guarantee optimality
up to $\epsilon=10^{-4}$.
A visual comparison of selected cases is shown in \Figref{visual}.

@@

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcc}
    \toprule
                    & Move-making & Exact \\
    \cmidrule{1-3}
    Dual Objective $o_\W$ &92.06& 92.24\\
    Estimated Objective $o^{\hat{I}}$ & 92.07 &92.24\\
    True Primal Objective $o^E$&92.35& 92.24  \\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Objective function values on the Pascal Dataset.}
    \tablabel{pascal_objective}
\end{table}

>>>>

In this chapter, we investigate the necessity and consequences of these
approximations in the $1$-slack cutting-plane learning algorithm in the context of semantic
image segmentation. We show that despite inference being deemed intractable in
loopy superpixel models, we are able to learn a pairwise conditional random
field model using a structured support vector machine exactly for this task.
We evaluate our approach on the popular MSRC-21 and \textsc{Pascal VOC} datasets. Our
approach improves upon the state-of-the-art on the MSRC-21 dataset, and is
competative with comparable approaches on the \textsc{Pascal VOC} dataset.% and nyu?

@@

\subsection{Semantic Image Segmentation}
% TODO reference auf davor / intro?
Our main application is of course semantic segmentation and object class
segmentation. We evaluate the proposed learning approach on \textsc{Pascal} VOC 2013 and
MSRC-21

@@

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lc}
        \toprule
                    & Jaccard \\
        \cmidrule{1-2}
    Unary terms only &  27.5 \\
    Pairwise model (move making)& 30.2\\
    Pairwise model (exact) & 30.4\\
        \cmidrule{1-2}
    \citet{dann2012pottics} & 27.4\\
    \citet{krahenbuhl2012efficient} & 30.2\\
    \citet{krahenbuhlparameter} & 30.8\\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Accuracies on the \textsc{Pascal} VOC Dataset. We compare our approach
    against approaches using the same unary potentials.\tablabel{pascalacc}}

@@

\subsubsection{Pascal VOC 2010}
For the \textsc{Pascal} VOC 2010 dataset, we follow the procedure from \citet{krahenbuhl2012efficient}
in using the official ``validation'' set as our evaluation set, and splitting the training set again.
We use the unary potentials provided by the same work, and compare only against methods
using the same setup and potentials, \citet{krahenbuhlparameter} and \citet{dann2012pottics}.
Note that state-of-the-art approaches, some not build on the CRF framework, obtain
around a Jaccard Index (also call VOC score) of 40\% , notably \cite{xia2012segmentation}, who 
evaluate on the \textsc{Pascal} VOC 2010 ``test'' set.

@@

Results on the \textsc{Pascal} VOC dataset are shown in \Tabref{pascalacc}.
We compare against several approaches using the same unary potentials.
For completeness, we also list state-of-the-art approaches not based on CRF models.
Notably, out model matches or exceeds the performance of the much more involved approaches of
\citet{krahenbuhl2012efficient} and \citet{dann2012pottics} which use the same
unary potentials.
Using exact learning and inference slightly increased performance on this dataset.
Learning took 25 minutes using move-making alone and 100 minutes to guarantee optimality
up to $\epsilon=10^{-4}$.
A visual comparison of selected cases is shown in \Figref{visual}.

@@

\begin{table}
    \begin{center}
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcc}
    \toprule
                    & Move-making & Exact \\
    \cmidrule{1-3}
    Dual Objective $o_\W$ &92.06& 92.24\\
    Estimated Objective $o^{\hat{I}}$ & 92.07 &92.24\\
    True Primal Objective $o^E$&92.35& 92.24  \\
    \bottomrule
    \end{tabularx}
    \end{center}
    \caption{Objective function values on the \textsc{Pascal} VOC Dataset.}
    \tablabel{pascal_objective}
\end{table}

### 2013-09-26 intro.tex
smallcaps for datasets, some more corrections by vlad

In the following we distinguish between the task of semantic segmentation,
which usually distinguishes unstructured ``stuff'' classes such as road and
grass, and object class segmentation, which denotes the segmentation of very
structured classes, such as cars, planes and people. We consider four
different datasets in this thesis: the object class segmentation datasets
Graz-02~\citep{marszatek2007accurate} and Pascal VOC 2010~\citep{pascal}, and
the semantic segmentation datasets MSRC-21~\citep{shotton2006textonboost} and
NYU V2~\citep{SilbermanECCV12}. Examples can be found in \Figref{pascal_msrc}.
%
Both tasks have the same ultimate goal of parsing, and therefore understanding,
images in terms of semantic classes. However they employ different mechanisms
to represent and process.

@@

\begin{figure}[t]
    \begin{center}
    \begin{tabu} to 0.8\linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{msrc_scene}&%
    \includegraphics[width=\linewidth]{msrc_scene_GT}\\
    \includegraphics[width=\linewidth]{pascal}&%
    \includegraphics[width=\linewidth]{pascal_gt}
    \end{tabu}
    \end{center}
\caption{%
    Examples from the MSRC-21 (top) and Pascal VOC (bottom) datasets with
    ground-truth annotation. MSRC-21 contains mostly texture classes, such as
    tree, building, street and sky, but also objects, like cars in this example.
    Pascal VOC contains only object classes, such as person, cat, table and
    bottle, and an additional background class (black).
\figlabel{pascal_msrc}}
\end{figure}

@@

The problem of learning with approximate inference is investigated in
Chapter~\ref{ch:exact_learning}.  We develop a strategy for efficient caching
and a combination of inference algorithms that allows us to learn SSVMs for
semantic image segmentation exactly, even though the involved factor graphs
contain many loops. We demonstrate our algorithm on the Pascal VOC 2010, where we are competative
with comparable approaches, and MSRC-21 datasets where we improve upon the state-of-the-art.

>>>>

In the following we distinguish between the task of semantic segmentation,
which usually distinguishes unstructured ``stuff'' classes such as road and
grass, and object class segmentation, which denotes the segmentation of very
structured classes, such as cars, planes and people. We consider four
different datasets in this thesis: the object class segmentation datasets
\textsc{Graz}-02~\citep{marszatek2007accurate} and \textsc{Pascal} VOC 2010~\citep{pascal}, and
the semantic segmentation datasets MSRC-21~\citep{shotton2006textonboost} and
NYU V2~\citep{SilbermanECCV12}. Examples can be found in \Figref{pascal_msrc}.
%
Both tasks have the same ultimate goal of parsing, and therefore understanding,
images in terms of semantic classes. However they employ different mechanisms
to represent and process.

@@

\begin{figure}[t]
    \begin{center}
    \begin{tabu} to 0.8\linewidth{@{}XX@{}}
    \includegraphics[width=\linewidth]{msrc_scene}&%
    \includegraphics[width=\linewidth]{msrc_scene_GT}\\
    \includegraphics[width=\linewidth]{pascal}&%
    \includegraphics[width=\linewidth]{pascal_gt}
    \end{tabu}
    \end{center}
\caption{%
    Examples from the MSRC-21 (top) and \textsc{Pascal} VOC (bottom) datasets with
    ground-truth annotation. MSRC-21 contains mostly texture classes, such as
    tree, building, street and sky, but also objects, like cars in this example.
    \textsc{Pascal} VOC contains only object classes, such as person, cat, table and
    bottle, and an additional background class (black).
\figlabel{pascal_msrc}}
\end{figure}

@@

The problem of learning with approximate inference is investigated in
Chapter~\ref{ch:exact_learning}.  We develop a strategy for efficient caching
and a combination of inference algorithms that allows us to learn SSVMs for
semantic image segmentation exactly, even though the involved factor graphs
contain many loops. We demonstrate our algorithm on the \textsc{Pascal} VOC 2010, where we are competative
with comparable approaches, and MSRC-21 datasets where we improve upon the state-of-the-art.

### 2013-09-26 itm/paper.tex
smallcaps for datasets, some more corrections by vlad

Table~\ref{results} summarizes the results. The two entropy-based methods 
(MeanNN, ITM) have a clear advantage of the other methods, with ITM finding 
better clusterings than MeanNN in the majority of cases.
We see that ITM does well when the intrinsic dimensionality of the data matches
the feature dimension, but degraded otherwise (see ``faces'' and ``usps'').
Estimating the intrinsic dimensionality of the data overcomes this weakness,
and improves results in most cases. For all but one dataset, either ITM or ITM with
estimated intrinsic dimensionality gives the best results of all considered
algorithms.
%
The single link agglomerative clustering procedure produces reasonable 
results on datasets with little noise and well-separated clusters, but 
fails otherwise.
%
The run time of computing the ITM clustering was dominated by the computation
of the MST of the data.
%
% TODO runtime statements!
% One table datasets, one table methods + runtime?

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lrrrccccc}
\toprule
\multicolumn{4}{c}{Dataset} &\multicolumn{4}{c}{Results}\\
\cmidrule{1-4}
\cmidrule{5-9}
Description &     n &    d &   k &  $k$-Means      & MeanNN        & SL            &   ITM        & ITM ID \\
\cmidrule{1-4}                   \cmidrule{5-5}    \cmidrule{6-6}  \cmidrule{7-7} \cmidrule{8-8} \cmidrule{9-9}
digits      &$ 1797$&$  64$&$ 10$& $    0.62 $&     $0.67$           &$0.10$         &$\mathbf{0.85}$       &$0.73$\\ 
faces       &$  400$&$4096$&$ 40$& $    0.41 $&     $0.49$           &$0.08$         &$0.02$           &$\B{0.54}$\\ 
iris        &$  150$&$   4$&$  3$& $    0.72 $&     $0.75$           &$0.55$         &$\B{0.88}$       &$0.88$\\
usps        &$ 9298$&$ 256$&$ 10$& $    0.52 $&     $0.54$           &$0.00$         &$   0.44$        &$\B{0.64}$\\ 
vehicle     &$  846$&$  18$&$  4$& $    0.10 $&     $0.09$           &$0.00$         &$\B{0.10}$       &$0.10$\\
vowel       &$  990$&$  10$&$ 11$& $    0.17 $&     $0.19$           &$0.00$         &$\B{0.20}$       &$0.19$\\
waveform    &$ 5000$&$  21$&$  2$& $\B{0.37} $&     $0.30$           &$0.00$         &$   0.23 $       &$0.23$\\
mnist       &$70000$&$ 784$&$ 10$& $    0.37 $&     N/A$^\dagger$    &$0.00$         &$   0.50$        &$\B{0.77}$\\
\bottomrule
\end{tabularx}
\caption{Adjusted Rand Index of $k$-Means, MeanNN, single link agglomerative
    clustering and ITM on several datasets (higher is better). ITM ID refers to
    ITM using the estimated intrinsic dimensionality. The best score for each
    dataset is printed in bold.\\$^\dagger$\footnotesize We were unable to make
    MeanNN scale to 70000 data points, as storing the whole pairwise distance
    matrix seems necessary.\label{results}}
\end{table}

>>>>

Table~\ref{results} summarizes the results. The two entropy-based methods 
(MeanNN, ITM) have a clear advantage of the other methods, with ITM finding 
better clusterings than MeanNN in the majority of cases.
We see that ITM does well when the intrinsic dimensionality of the data matches
the feature dimension, but degraded otherwise (see \textsc{faces} and \textsc{usps}).
Estimating the intrinsic dimensionality of the data overcomes this weakness,
and improves results in most cases. For all but one dataset, either ITM or ITM with
estimated intrinsic dimensionality gives the best results of all considered
algorithms.
%
The single link agglomerative clustering procedure produces reasonable 
results on datasets with little noise and well-separated clusters, but 
fails otherwise.
%
The run time of computing the ITM clustering was dominated by the computation
of the MST of the data.
%
% TODO runtime statements!
% One table datasets, one table methods + runtime?

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lrrrccccc}
\toprule
\multicolumn{4}{c}{Dataset} &\multicolumn{4}{c}{Results}\\
\cmidrule{1-4}
\cmidrule{5-9}
Description &     n &    d &   k &  $k$-Means      & MeanNN        & SL            &   ITM        & ITM ID \\
\cmidrule{1-4}                   \cmidrule{5-5}    \cmidrule{6-6}  \cmidrule{7-7} \cmidrule{8-8} \cmidrule{9-9}
\textsc{digits}      &$ 1797$&$  64$&$ 10$& $    0.62 $&     $0.67$           &$0.10$         &$\mathbf{0.85}$       &$0.73$\\ 
\textsc{faces}       &$  400$&$4096$&$ 40$& $    0.41 $&     $0.49$           &$0.08$         &$0.02$           &$\B{0.54}$\\ 
\textsc{iris}        &$  150$&$   4$&$  3$& $    0.72 $&     $0.75$           &$0.55$         &$\B{0.88}$       &$0.88$\\
\textsc{usps}        &$ 9298$&$ 256$&$ 10$& $    0.52 $&     $0.54$           &$0.00$         &$   0.44$        &$\B{0.64}$\\ 
\textsc{vehicle}     &$  846$&$  18$&$  4$& $    0.10 $&     $0.09$           &$0.00$         &$\B{0.10}$       &$0.10$\\
\textsc{vowel}       &$  990$&$  10$&$ 11$& $    0.17 $&     $0.19$           &$0.00$         &$\B{0.20}$       &$0.19$\\
\textsc{waveform}    &$ 5000$&$  21$&$  2$& $\B{0.37} $&     $0.30$           &$0.00$         &$   0.23 $       &$0.23$\\
\textsc{MNIST}       &$70000$&$ 784$&$ 10$& $    0.37 $&     N/A$^\dagger$    &$0.00$         &$   0.50$        &$\B{0.77}$\\
\bottomrule
\end{tabularx}
\caption{Adjusted Rand Index of $k$-Means, MeanNN, single link agglomerative
    clustering and ITM on several datasets (higher is better). ITM ID refers to
    ITM using the estimated intrinsic dimensionality. The best score for each
    dataset is printed in bold.\\$^\dagger$\footnotesize We were unable to make
    MeanNN scale to 70000 data points, as storing the whole pairwise distance
    matrix seems necessary.\label{results}}
\end{table}

### 2013-09-26 main.tex
some graphics, minor fixes.
smallcaps for datasets, some more corrections by vlad

We showed that effective use of available inference mechanisms enables
exact learning, even in the presence of loops in the underlying
factor graph. Our methods achieve competitive performance with similar
 methods on the Pascal VOC 2010 dataset, and improve upon state-of-the-art
 results on the MSRC-21 dataset.
We demonstrated the power of conditional interactions by learning spatial
interactions in an RGB-D setting. Here, our approach improves upon the state-of-the
art on the NYU V2 benchmark for annotation of semantic structure classes.

We also presented a novel approach for clustering based on information
theoretic principles. Our algorithm improves upon methods from the literature
in finding pre-defined classes on a wide range of datasets. This indicates that
in the task of extracting superpixels, we can also hope to achieve better
results than the $k$-means based SLIC algorithm that we used.
\enlargethispage{1cm}
As manual annotation of images for learning semantic segmentation and object
class recognition is laborious and error-prone, we suggested a method to
learn object class segmentation for complex object classes from image-level
annotations alone. Our approach is formulated using multiple instance learning
over a set of candidate segments. We demonstrated the feasibility and effectiveness
of our approach on the challenging Graz-02 dataset of street scenes.

@@

\paragraph{Theoretical Analysis of $n$-slack Algorithm}

>>>>

We showed that effective use of available inference mechanisms enables
exact learning, even in the presence of loops in the underlying
factor graph. Our methods achieve competitive performance with similar
methods on the \textsc{Pascal} VOC 2010 dataset, and improve upon state-of-the-art
 results on the MSRC-21 dataset.
We demonstrated the power of conditional interactions by learning spatial
interactions in an RGB-D setting. Here, our approach improves upon the state-of-the
art on the NYU V2 benchmark for annotation of semantic structure classes.

We also presented a novel approach for clustering based on information
theoretic principles. Our algorithm improves upon methods from the literature
in finding pre-defined classes on a wide range of datasets. This indicates that
in the task of extracting superpixels, we can also hope to achieve better
results than the $k$-means based SLIC algorithm that we used.
\enlargethispage{1cm}
As manual annotation of images for learning semantic segmentation and object
class recognition is laborious and error-prone, we suggested a method to
learn object class segmentation for complex object classes from image-level
annotations alone. Our approach is formulated using multiple instance learning
over a set of candidate segments. We demonstrated the feasibility and effectiveness
of our approach on the challenging \textsc{Graz}-02 dataset of street scenes.

@@

\paragraph{Theoretical Analysis of the $n$-Slack Algorithm}

### 2013-09-26 nyu/paper.tex
smallcaps for datasets, some more corrections by vlad

We evaluate our approach on the public NYU depth V2 segmentation dataset of
indoor scenes.  The dataset comes with a detailed annotation of 1449 indoor
\mbox{RGB-D} images belonging to a wide variety of indoor scenes, categorized into 26
scene classes.  The annotation contains four semantic structural classes:
structure, floor, furniture and prop. As in the MSRC-21 and Pascal VOC
datasets, there is an additional ``void'' class, which is used for object
boundaries and hard-to-annotate regions. We follow the
literature in excluding these pixels completely from the evaluation.
We optimize our model for \emph{average class accuracy} (the mean of the
diagonal of the confusion matrix), which puts more emphasis on the harder
classes of props and furniture, which have smaller area than structure and
floor.

>>>>

We evaluate our approach on the public NYU depth V2 segmentation dataset of
indoor scenes.  The dataset comes with a detailed annotation of 1449 indoor
\mbox{RGB-D} images belonging to a wide variety of indoor scenes, categorized into 26
scene classes.  The annotation contains four semantic structural classes:
structure, floor, furniture and prop. As in the MSRC-21 and \textsc{Pascal} VOC
datasets, there is an additional ``void'' class, which is used for object
boundaries and hard-to-annotate regions. We follow the
literature in excluding these pixels completely from the evaluation.
We optimize our model for \emph{average class accuracy} (the mean of the
diagonal of the confusion matrix), which puts more emphasis on the harder
classes of props and furniture, which have smaller area than structure and
floor.

### 2013-09-26 partial_supervision/paper.tex
smallcaps for datasets, some more corrections by vlad

\section{Related Work}
\subsection{Object Segment Proposals}\label{related_segments}
Most work on multi-class segmentation focuses on strong supervision on
superpixel level. There is still little work on using candidate segments.  The
method we use for generating candidate segments is Constraint Parametric
Min-Cuts (CPMC) from \citet{carreira2010constrained}.  This method creates a
wide variety of overlapping segments. Support vector regression (SVR) is
trained on these segments to estimate the overlap of segments with ground truth
object-class labeling from the Pascal VOC dataset~\citep{pascal}. This provides
a ranking of candidate segments according to how ``object-like'' they are,
which allows for selecting only a limited number of very object-like segments.
The method performed well on a variety of datasets, building the basis of
a very successful entry to the Pascal VOC segmentation
challenge~\citep{li2010object}. A similar approach to whole-object segment
proposals was investigated by \citet{endres2010category}, but they did not compare
their results with the state-of-the-art approach of \citet{carreira2010constrained}.
%Brendel and Todorovic~\citet{NIPS2010_0122} also use a set of candidate segments is used, though all of these are kept throughout the whole 
%algorithm.

@@

We evaluate the performance of the proposed algorithm for object-class
segmentation on the challenging Graz-02 dataset~\citep{marszatek2007accurate}.  This dataset contains 1096
images of three object classes, bike, car and person.  Each image may contain
multiple instances of the same class, but only one class is present per image.

@@

\begin{figure}[tbp]
	\begin{center}
        \includegraphics[width=35mm]{images/car1_img.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_neg.png}\hspace*{0.7ex}\\
        \vspace{1mm}
        \includegraphics[width=35mm]{images/person1_img.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_neg.png}
	\end{center}
        \caption{Qualitative results on on the Graz-02 dataset. Top: Results on
        category ``car''. Bottom: Results on category ``person''. From left to
        right: original image, ground truth segmentation, segment votes for
        correct class, segment votes against correct class (red many, blue few votes).}
	\figlabel{results}
\end{figure}

\begin{table}
    \centering
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}p{208pt}ccc}
    \toprule
                & car & bike & person \\
    \cmidrule{2-4}
        MIL-MKL (our approach)&   0.30&  0.45&  0.43 \\
        Best strongly supervised approaches~\citep{fulkerson2009class,schulz2011}&   0.72&  0.72&  0.66 \\
    \bottomrule
    \end{tabularx}
    \caption{Pixel-level accuracy on the Graz-02 dataset.
        \tablabel{tab:graz}}
\end{table}

@@

We evaluated the proposed object-class segmentation method on the challenging
Graz-02 dataset. While not reaching the performance of methods using strong
supervision, our result can work as a baseline for further research into weakly
supervised object-class segmentation.

>>>>

\section{Related Work}
\subsection{Object Segment Proposals}\label{related_segments}
Most work on multi-class segmentation focuses on strong supervision on
superpixel level. There is still little work on using candidate segments.  The
method we use for generating candidate segments is Constraint Parametric
Min-Cuts (CPMC) from \citet{carreira2010constrained}.  This method creates a
wide variety of overlapping segments. Support vector regression (SVR) is
trained on these segments to estimate the overlap of segments with ground truth
object-class labeling from the \textsc{Pascal} VOC dataset~\citep{pascal}. This provides
a ranking of candidate segments according to how ``object-like'' they are,
which allows for selecting only a limited number of very object-like segments.
The method performed well on a variety of datasets, building the basis of
a very successful entry to the \textsc{Pascal} VOC segmentation
challenge~\citep{li2010object}. A similar approach to whole-object segment
proposals was investigated by \citet{endres2010category}, but they did not compare
their results with the state-of-the-art approach of \citet{carreira2010constrained}.
%Brendel and Todorovic~\citet{NIPS2010_0122} also use a set of candidate segments is used, though all of these are kept throughout the whole 
%algorithm.

@@

We evaluate the performance of the proposed algorithm for object-class
segmentation on the challenging \textsc{Graz}-02 dataset~\citep{marszatek2007accurate}.  This dataset contains 1096
images of three object classes, bike, car and person.  Each image may contain
multiple instances of the same class, but only one class is present per image.

@@

\begin{figure}[tbp]
	\begin{center}
        \includegraphics[width=35mm]{images/car1_img.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/car1_neg.png}\hspace*{0.7ex}\\
        \vspace{1mm}
        \includegraphics[width=35mm]{images/person1_img.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_gt.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_pos.png}\hspace*{0.7ex}
        \includegraphics[width=35mm]{images/person1_neg.png}
	\end{center}
    \caption{Qualitative results on on the \textsc{Graz}-02 dataset. Top: Results on
        category ``car''. Bottom: Results on category ``person''. From left to
        right: original image, ground truth segmentation, segment votes for
        correct class, segment votes against correct class (red many, blue few votes).}
	\figlabel{results}
\end{figure}

\begin{table}
    \centering
    \begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}p{208pt}ccc}
    \toprule
                & car & bike & person \\
    \cmidrule{2-4}
        MIL-MKL (our approach)&   0.30&  0.45&  0.43 \\
        Best strongly supervised approaches~\citep{fulkerson2009class,schulz2011}&   0.72&  0.72&  0.66 \\
    \bottomrule
    \end{tabularx}
    \caption{Pixel-level accuracy on the \textsc{Graz}-02 dataset.
        \tablabel{tab:graz}}
\end{table}

@@

We evaluated the proposed object-class segmentation method on the challenging
\textsc{Graz}-02 dataset. While not reaching the performance of methods using strong
supervision, our result can work as a baseline for further research into weakly
supervised object-class segmentation.

### 2013-09-26 pystruct/paper.tex
smallcaps for datasets, some more corrections by vlad

\paragraph{Efficiency}
     While \pystruct focuses on usability, providing efficient and competitive
     implementations is important to allow fast prototyping and scaling to
     large datasets. \pystruct achieves the same runtime performance
     as the popular \svmstruct model for cutting plane algorithms, and
     provides implementations of the BCFW and Subgradient methods that scale to
     large datasets.

@@

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the Pascal dataset. Details of the experiment
can be found in Section~\secref{semantic_segmentation}.
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')

>>>>

\paragraph{Efficiency}
     While \pystruct focuses on usability, providing efficient and competitive
     implementations is important to allow fast prototyping and scaling to
     large datasets. \pystruct achieves the same runtime performance
     as the popular \svmstruct model for cutting plane algorithms, and
     provides implementations of the SZLJSP and Subgradient methods that scale to
     large datasets.

@@

We demonstrate the use of \pystruct on the task of semantic image segmentation,
the main focus of this work. The example shows how to learn an $n$-slack support
vector machine on a superpixel-based CRF on the \textsc{Pascal VOC} dataset. Details of the experiment
can be found in Section~\secref{semantic_segmentation}.
Each sample (corresponding on one entry of the list \texttt{X}) is represented as a
tuple consisting of input features and a graph representation.
\begin{listing}[t]
\begin{pythoncode}
model = crfs.EdgeFeatureGraphCRF(
            class_weight=inverse_frequency,
            symmetric_edge_features=[0, 1],
            antisymmetric_edge_features=[2],
            inference_method='qpbo')
